Development of a 3D display

### 2016-05-17 paper.tex
Conclusions & outlook

\item Size: At most $\SI{5}{\milli\meter}$ by $\SI{5}{\milli\meter}$, preferably smaller, but
still large enough to solder by hand

@@

A positive side effect of placing some vias beneath the chip is their thermal conductivity. That
way, the chips' waste heat can be dissipated more effectively. The maximum power output of the
chips --- when all the attached LEDs are turned on --- is as follows:

@@

To fix this I added a boolean variable called \texttt{running}, which is set to \texttt{false} by
default and only flipped when the magnet is first detected. That way the program only starts
running if the display is actually rotating, at which point we can be sure that power is supplied
through the sliprings rather than the USB port.

@@

Because the slip rings weren't fixed in their position, they could slide out of their slots after
a few minutes of operation. I fixed this issue by mounting a small wooden board onto these slots
(perventing lateral movement), and routing the cables going from the power supply to the sliprings
through two holes in that board (perventing lengthwise movement).

@@

>>>>

\item Size: At most \SI{5}{\milli\meter} by \SI{5}{\milli\meter}, preferably smaller, but still
large enough to solder by hand

@@

A positive side effect of placing some vias beneath the chip is their thermal conductivity, which
helps disspiate the chip's excess heat. The maximum power output of the chips --- when all the
attached LEDs are turned on --- is as follows:

@@

To fix this I added a boolean variable called \texttt{running}, which is set to \texttt{false} by
default and only flipped when the magnet is first detected. That way the program only starts
running if the display is actually rotating, at which point we can be sure that power is supplied
through the slip rings rather than the USB port.

@@

Because the slip rings weren't fixed in their position, they could slide out of their slots after
a few minutes of operation. I fixed this issue by mounting a small wooden board onto these slots
(perventing lateral movement), and routing the cables going from the power supply to the slip rings
through two holes in that board (perventing lengthwise movement).

@@

\chapter{Conclusions}

\section{Possible Improvements}

\subsection{Controller and Data Transmission}

The Teensy 3.1 is currently mounted quite loosely on its wooden disc. A piece of wire goes through
two unoccupied contacts as well as through two holes in the disc. In addition, the cables forming
the SPI bus aren't laid out neatly at all; many are too long and don't take the direct route.

This situation could be improved by replacing the upper wooden disc with another printed circuit
board. All connections could be routed elegantly on the PCB, and the SPI interfaces could be
formed by two ribbon cables. The hall sensor could be properly soldered on instead of fixing it in
place using hot glue.

Between the individual LED boards, ribbon cables could also be considered. However, the only
connections that always go to the board right above are CLK, LE and OE, while the serial data
inputs and outputs have to be connected to the board on the opposite side. These connections would
still have to be formed by individual cables.

Because the slip rings are quite rough and not completely horizontal, a lot of pressure is needed
to form a consistent contact. This leads to high friction between the two contacts, which then
results in quick wear as well as a lot of friction.

The main reason why the display is not energy efficient at all are the slip rings. At the start of
the project, I had the idea of using a \SI{3.5}{\milli\meter} phone connector to transmit power.
However, I abolished that plan because of two reasons. Firstly, I had concerns that such a small
connector would have trouble conducting the maximum current of \SI{10}{\ampere}. This would most
likely not have been a problem, since only a small part of all pixels are turned on in a typical
image, which causes the average current to be a small fraction of the maximum value.

The second problem would've been the difficulty of mounting a phone connector on the display. I
would've had to place it at the end of the shaft, where it would've also served as a bearing. In
order to minimise the forces acting upon the plug, it would've had to be mounted exactly in the
center of the shaft. I couldn't come up with a solid way to connect both of the phone plugs' ends
to the display.

A much more elegant solution would've been to use induction to transfer power. By having a
stationary and a rotating coil close together, I could've passed a high-frequency alternating
current through the stationary one, causing current to flow in the rotating one as well. The
advantages of such an approach would be substantial: The bearings would be the only contact point
between the rotating and stationary part, causing friction to be minimal. I could've also
completely eliminated the annoying, broadband noise currently emitted by the slip rings.

I didn't implement wireless power transfer because I felt like the extra work wasn't worth it,
especially considering this was a prototype. If I wanted to produce this display en masse,
inductive power transfer would definitely be the way to go as it's the only way to make the
display somewhat quiet.

I decided to drive the display directly without any kind of gear reduction because that was the
simplest solution. I only could do so because the motor was strong enough. Unfortunately, it
consumes a substantial amount of current.

If I wanted to sell my display commercially, I'd use a smaller motor, drive it at a higher
rotational speed and gear it down. To save energy, I would also implement one of the above
imporvements concerning power transmission.

\section{Future Outlook}

\subsection{Animated images}

Something I had in mind since the beginning of this project were animated images. The Teensy 3.1
has \SI{256}{\kilo\byte} of memory, which would fit 42 images of \SI{6}{\kilo\byte} each. This
corresponts to roughly a second of playback. In order to display longer animations, there are
several workarounds: Instead of showing one image that spans the entirety of the rotation, I can
instead only save an image that is 25 pixels and display it four times.

In order to get around the limit of flash memory, external storage would be necessary. Even with
only \SI{1}{\giga\byte}, I could save 166666 frames, thus removing any practical limit in terms of
playback time.

\subsection{Interactive Programs}

It would be interesting to not only display predefined images, but to actually run a program that
can respond to user input, like a video game. In order to communicate with the external world, a
wireless interface would be necessary. Readily available solutions include small WLAN or bluetooth
modules, or the transmitters and receivers commonly used in radio-controlled aircraft.

\subsection{Applications}

Because of the low resolution and colour depth, the high level of noise, quick wear and the
inability to send images to the display while running, this display is not suited as a replacement
for your everyday computer or TV screen. However, these problems can all be fixed completely or
partially, so that there could one day exist a version of my display which is actually suitable
for the above purposes.

One domain where I could imagine a display like mine being especially useful is advertising.
Because most people haven't ever seen such a display before, it would be an immediate eye-catcher
in the display window of any business.

Another possibility would be video games. Although the limited resolution and computing power
would make it difficult to run the newest games, 3D version of classics like Pong, Snake or a
simple platform game would be worth a shot.
